Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
Updating Q2 example and adding changes from meeting

\begin{table}[h!]
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
      \cmidrule{2-3}
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.}
    \label{tab:quadrants}
  \end{center}
\end{table}

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Thm.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Lem.~\ref{lem:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Lemma~\ref{lem:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).}
\label{fig:results-flow}
\end{figure}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
We can then leverage the contrapositive of this result: if $\gamma$ has a level set intricate enough not to contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent convex surrogate.

@@

The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.  I know, weird.}
% Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which 
A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Lemma~\ref{lem:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.

\begin{lemma}
  \label{lem:convex-flats-inf-dim}
  Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
  \footnote{This assumption is largely for technical convenience, to ensure that $\V_{u,p}$ does not depend on $p$.
    Any such assumption would suffice, and we suspect even that condition can be relaxed.}
  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
  \jessiet{Change back to Theorem?}
  \raft{Good to discuss; let's leave as Lemma for now}
\end{lemma}
\begin{proof}
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  We proceed in two cases, depending on $|\Y|$.

@@

Lemma~\ref{lem:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
Proofs are deferred to Appendix~\ref{app:implications-of-bounds}.

@@

\subsection{Illustrating the condition in all four quadrants}
\label{sec:illustration}
We now illustrate how to apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.  But I'm thinking we'll want to bring them back actually, and state the Cor's below Lem 1... let's discuss on Monday}
% by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
% The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Table~\ref{tab:quadrants-simplices}).
For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.

@@

To apply Lemma~\ref{lem:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
% Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
For the depicted distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension as we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, which matches the upper bound from the convex surrogate of
\citet{ramaswamy2016convex}.\raft{Jessie: see if you can match the style of the revised abstain example for the others.  In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.  Probably it's only Q2 that needs to change. \jessie{Took a pass! Feel free to burn}}
%present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.

\paragraph{Q2: High confidence classification.}
Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.

We can now model this problem by a property with the reports $\R = \Y$, and have 
\begin{align*}
\gamma(p) &= \begin{cases}
\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
\end{cases}~,~
\end{align*}

This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
Therefore, we can apply Lemma~\ref{lem:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.

\paragraph{Q3: Least-squares regression}
%\jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).
Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Table~\ref{tab:quadrants-simplices}.

@@

\begin{SCtable}
\begin{tabular}{c|c}
	%\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${\text{rainy}}$] (h) at (1,0,0);
	\coordinate[label=below:${\text{sunny}}$] (m) at (0,1,0);
	\coordinate[label=right:${\text{snowy}}$] (l) at (0,0,1);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
	\def\e{1/16};
	\draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\gamma_{\text{rainy}}$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\gamma_{\text{snowy}}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[orange, thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (point) at (0.3,0.4,0.3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.05}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.

@@

In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Lemma~\ref{lem:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.

The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.

@@

\section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}
In order to apply Lemma~\ref{lem:convex-flats-inf-dim} to various properties, we need the following lemmas about separating hyperplanes.

>>>>

\begin{table}[h!]
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
      \cmidrule{2-3}
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.}
    \label{tab:quadrants}
  \end{center}
\end{table}

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results, while simultaneously applying to other settings (Q2,4).}
\label{fig:results-flow}
\end{figure}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
We can then leverage the contrapositive of this result: if $\gamma$ has a level set intricate enough not to contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent convex surrogate.

@@

The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}.\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.  I know, weird.}
% Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which 
A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem~\ref{thm:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.

\begin{restatable}{theorem}{convexflats}  \label{thm:convex-flats-inf-dim}
  Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
  \footnote{This assumption is largely for technical convenience, to ensure that $\V_{u,p}$ does not depend on $p$.
    Any such assumption would suffice, and we suspect even that condition can be relaxed.}
  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{restatable}
\begin{proof}[Sketch]
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  Here, we show the result for finite $\Y$, and defer the full proof to Appendix~\ref{app:implications-of-bounds}.
  With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
  Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
  Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
  Observe that $\E_p V_{u,p} = \vec 0$.				 
  We take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
  To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
\end{proof}

@@

Theorem~\ref{thm:convex-flats-inf-dim} now allows us to derive bounds on convex consistency dimension by considering distributions and property values that are either single-valued (Corollary~\ref{cor:Pcodim-flat-single-val-prop}) or on the relative interior of the simplex with finite $\Y$ (Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}).
Proofs are deferred to Appendix~\ref{app:implications-of-bounds}.

@@

\subsection{Illustrating the condition in all four quadrants}
\label{sec:illustration}
We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.\raft{I once again cut mention of the Corollaries, hoping we can use the lemma directly for these examples.  But I'm thinking we'll want to bring them back actually, and state the Cor's below Lem 1... let's discuss on Monday}
% by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
% The illustrations in Figure~\ref{fig:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Figure~\ref{fig:quadrants-simplices}).
For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.

@@

To apply Theorem~\ref{thm:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
% Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
For the depicted distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension as we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, which matches the upper bound from the convex surrogate of
\citet{ramaswamy2016convex}.\raft{Jessie: see if you can match the style of the revised abstain example for the others.  In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.  Probably it's only Q2 that needs to change. \jessie{Took a pass! Feel free to burn}}
%present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.

\paragraph{Q2: Variation of hierarchical classification.}
\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
\citet{ramaswamy2015hierarchical} studies a discrete target loss for hierarchical classification tasks~\citep{xiao2007hierarchical,burkhardt2005database}, such as the task in Figure~\ref{fig:hierarchical-tree}, in which one wishes to predict the deepest node in a tree that is ``likely enough.''
Consider the mild variation of this task where one wants to predict an outcome if it is likely enough, and otherwise proceed in a different direction and classify from another binary substructure as depicted in Figure~\ref{fig:quadrants-simplices} (Q2). 
Here, we take the reports and outcomes $\R = \Y$ to be the leaves of the tree in Figure~\ref{fig:hierarchical-tree}.
\citet{osband1985providing} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belongs in Q2.

We can now model this problem by a property with the reports $\R = \Y$, and have 
\begin{align*}
\gamma(p) &= \begin{cases}
\text{active} & p_{\text{active}} \geq 1/2 \\
\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
\end{cases}~,~
\end{align*}

\begin{SCfigure}
	\centering
	\begin{tikzpicture}
\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=4pt, fill = white];
\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=4pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
\tikzstyle{every node}=[font=\small];

% vertices
\node[vertex] (speech) at  (0,2) {Speech};
\node[vertexblue] (active) at  (-2,1) {Active};
\node[vertex] (nonactive) at  (2,1) {Non-active};
\node[vertexblue] (median) at  (1,0) {Median};
\node[vertexblue] (passive) at  (3,0) {Passive};

%edges
\draw[thick] (speech) --(active);
\draw[thick] (speech) --(nonactive);
\draw[thick] (median) --(nonactive);
\draw[thick] (passive) --(nonactive);
	\end{tikzpicture}
	\caption{Hierarchical prediction example with labeling tone of speech.  We take $\Y = \R$ to be the leaves of this tree, shown in blue.}
	\label{fig:hierarchical-tree}
\end{SCfigure}

In Figure~\ref{fig:quadrants-simplices} (Q2), we see that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through $p$.
Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
\jessiet{Old narrative in comment}
%Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
%Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
%\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
%
%We can now model this problem by a property with the reports $\R = \Y$, and have 
%\begin{align*}
%\gamma(p) &= \begin{cases}
%\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
%\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
%\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
%\end{cases}~,~
%\end{align*} 
%
%This property is shown in Figure~\ref{fig:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
%Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.

\paragraph{Q3: Least-squares regression}
%\jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Figure~\ref{fig:quadrants-simplices} (Q3).
Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Figure~\ref{fig:quadrants-simplices}.

@@

\begin{SCfigure}
\begin{tabular}{c|c}
	%\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${\text{passive}}$] (h) at (1,0,0);
	\coordinate[label=below:${\text{median}}$] (m) at (0,1,0);
	\coordinate[label=right:${\text{active}}$] (l) at (0,0,1);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
	\def\e{1/16};
	\draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
\draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (point) at (0.3,0.4,0.3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.05}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.

@@

In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.

The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.

@@

\section{Implications of convex indirect elicitation bounds}\label{app:implications-of-bounds}

We start by fully proving Theorem~\ref{thm:convex-flats-inf-dim}.
\convexflats*
\begin{proof}
	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
	We proceed in two cases, depending on $|\Y|$.

In order to apply Theorem~\ref{thm:convex-flats-inf-dim} to various properties, we need the following lemmas about separating hyperplanes.
